```{r, message = FALSE}
library(tidyverse)
library(jsonlite)
```

# Find evolutions through API
# Find evolutions through scraping

# Find Pokemon start (what generation they were introduced)

#Request: Single Pokemon
```{r}
No = 1
r <- GET(str_glue("https://pokeapi.co/api/v2/evolution-chain/{id}/", id = No))
j <- content(r, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)

(stage2 <- j$chain$evolves_to$species.name)
(stage3 <- j$chain$evolves_to$evolves_to[[1]]$species.name)

r2 <- GET(str_glue("https://pokeapi.co/api/v2/evolution-chain"), query = list(limit = 1000))
j2 <- content(r2, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE) 
j2$count
```

#Iterate through basic Pokemon (API) - difficult
- try chain statement
```{r}
evols <- data.frame(Basic = character(),
                    Stage2 = character(),
                    Stage3 = character())

getEvols <- function(No){
  r <- GET(str_glue("https://pokeapi.co/api/v2/evolution-chain/{id}/", id = No))
  j <- content(r, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
  
  s2 = j$chain$evolves_to$species.name
  s3 = j$chain$evolves_to$evolves_to[[1]]$species.name
  
  try({
    print(No)
    df <- data.frame(NatNo = No, Stage2 = s2, Stage3 = s3)
    silent = TRUE
    outFile = "errors"})
  df
}

#works but needs to configuration for no evolutions and one other evolution
evols <- sapply(1:208, function(mon) getEvols(mon))

evols <- bind_rows(evols)
evols %>% (str_detect(NatNo,"\\d"))
```

# Scrape evolution chains - easy 
- as_tibble(.name_repair)
```{r}
h <- read_html("https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_evolution_family")
genFam <- h %>% 
  html_nodes("table.roundy") %>% 
  .[[2]] %>% 
  html_table(fill = TRUE) %>% 
  as_tibble(.name_repair = "unique")

genFam <- genFam %>% 
  select(2,5,8) %>% 
  rename(
    Basic = names(genFam)[2],
    Stage2 = names(genFam)[5],
    Stage3 = names(genFam)[8]
  ) %>% 
  filter(!str_detect(Basic,"family"))
```

```{r}

getGenFams <- function(i){
  h <- read_html("https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_evolution_family")
  genFam <- h %>% 
  html_nodes("table.roundy") %>% 
  .[[i]] %>% 
  html_table(fill = TRUE) %>% 
  as_tibble(.name_repair = "unique")

genFam <- genFam %>% 
  select(2,5,8) %>% 
  rename(
    Basic = names(genFam)[2],
    Stage2 = names(genFam)[5],
    Stage3 = names(genFam)[8]
  ) %>% 
  filter(!str_detect(Basic,"family"))
}

allGenFams <- lapply(1:8, function(x) getGenFams(x)) %>% bind_rows()

save(allGenFams,  file = "allFams.RData")
```

# Not left_join b/c we also want to observe prior evolutions

- consider those with two evolution paths (Poliwhirl, Nidoran)
- consider evolutions not introduced in the selected generation
```{r}
AM <- (getAreaMons("hoenn-route-102-area"))
(AM_evs <- allGenFams %>% 
  filter(Basic %in% AM$Pokemon | Stage2 %in% AM$Pokemon | Stage3 %in% AM$Pokemon))

(test <- allMons %>% filter(Gen > 3) %>% pull(Name))
"Gallade" %in% test$Name

allGenFams %>% 
  filter(Basic == "Ralts") %>% 
  filter(!Stage3 %in% (allMons %>% filter(Gen > 3) %>% pull(Name))) %>% 
  unlist() %>% 
  unique() 
```