```{r, message = FALSE}
library(tidyverse)
library(httr)
library(rvest)
library(jsonlite)
library(parallel)
```

# Function for getting learnset for Pokemon in a specific generation
 - scrape learnsets
 - scrape learnsets of different formes

# Issues
 - Category based on types prior to generation 3
 - Inconsistent column names
 - Learned
  - tryCatch statement returns stuff
  
```{r function}
# Mon = "Gallade"
# gen = "VI"

# https://bulbapedia.bulbagarden.net/wiki/Melmetal_(Pok%C3%A9mon)/Generation_VII_learnset#By_TM.2FHM

Mon <- "Magikarp"
gen <- "III"

# Special cases: MelMetal, Meltan, MissingNo
getLearnset <- function(Mon, gen = "III") {
  if (Mon %in% c("Melmetal", "Meltan")) {
    link <- "https://bulbapedia.bulbagarden.net/wiki/{mon}_(Pok%C3%A9mon)/Generation_{gen}_learnset#By_TM.2FHM"
  } else {
    link <- "https://bulbapedia.bulbagarden.net/wiki/{mon}_(Pok%C3%A9mon)/Generation_{gen}_learnset#By_leveling_up"
  }
  h <- read_html(str_glue(link,
                          mon = Mon, gen = gen
  ))
  
  gen <- case_when(
    gen == "I" ~ 1,
    gen == "II" ~ 2,
    gen == "III" ~ 3,
    gen == "IV" ~ 4,
    gen == "V" ~ 5,
    gen == "VI" ~ 6,
    gen == "VII" ~ 7,
    gen == "VIII" ~ 8,
    TRUE ~ 0
  )
  
  # By Level
  if (gen > 3) {
    byLevel <- h %>%
      html_node("table.sortable") %>%
      html_table() %>%
      as.data.frame() %>%
      select(1, Move, Type, `Cat.`, `Pwr.`, `Acc.`, PP)
    
    colnames(byLevel) <- c("Level", "Move", "Type", "Cat.", "Pwr.", "Acc.", "PP")
  } else {
    byLevel <- h %>%
      html_node("table.sortable") %>%
      html_table() %>%
      as.data.frame()
    
    byLevel <- tryCatch({
      byLevel <- byLevel %>%
        select(1, Move, Type, Power, Accuracy, PP) %>%
        mutate(`Cat.` = "Depends on Type")
    },error = function(err){
        byLevel <- byLevel %>%
          select(1, Move, Type, `Pwr.`, `Acc.`, PP) %>%
          mutate(`Cat.` = "Depends on Type")
    },warning = function(cond){
      message("Try something else")
    })
    
    colnames(byLevel) <- c("Level", "Move", "Type", "Pwr.", "Acc.", "PP", "Cat.")
    # if (gen < 3) {
    #   byLevel <- byLevel %>%
    #     select(1, Move, Type, Power, Accuracy, PP) %>%
    #     mutate(`Cat.` = "Depends on Type")
    # } else {
    #   byLevel <- byLevel %>%
    #     select(1, Move, Type, `Pwr.`, `Acc.`, PP) %>%
    #     mutate(`Cat.` = "Depends on Type")
    #}
    colnames(byLevel) <- c("Level", "Move", "Type", "Pwr.", "Acc.", "PP", "Cat.")
  }
  
  # Fix up values
  byLevel <- byLevel %>%
    mutate(
      Level = substring(Level, 0, nchar(as.character(Level)) / 2),
      `Pwr.` = as.character(`Pwr.`),
      PP = as.character(PP),
      Method = "Level"
    ) %>%
    as_tibble()
  
  
  # By Machine
  if (gen > 3) {
    byMachine <- h %>%
      html_nodes("table.roundy") %>%
      .[[3]] %>%
      html_table(fill = TRUE) %>%
      as_tibble() %>%
      slice(5:nrow(.)) %>%
      select(3:8)
    colnames(byMachine) <- c("Move", "Type", "Cat.", "Pwr.", "Acc.", "PP")
  } else {
    byMachine <- h %>%
      html_nodes("table.roundy") %>%
      .[[3]] %>%
      html_table(fill = TRUE) %>%
      as_tibble() %>%
      slice(5:nrow(.)) %>%
      select(3:7) %>%
      mutate(cat = "Depends on Type")
    colnames(byMachine) <- c("Move", "Type", "Pwr.", "Acc.", "PP", "Cat.")
  }
  
  
  
  byMachine <- byMachine %>%
    as_tibble() %>%
    mutate(
      Level = "",
      Method = "Machine"
    )
  
  if (Mon %in% c("Meltan", "Melmetal")){
    byBreed <- tibble(
      Move = "NA",
      Type = "NA",
      `Pwr.` = "NA",
      `Acc.` = "NA",
      PP = "NA",
      `Cat.` = "NA",
    )
  } else if (gen > 3) {
    byBreed <- h %>%
      html_nodes("table.roundy") %>%
      .[[5]] %>%
      html_table(fill = TRUE) %>%
      as_tibble() %>%
      slice(5:nrow(.)) %>%
      select(2:7)
    
    colnames(byBreed) <- c("Move", "Type", "Cat.", "Pwr.", "Acc.", "PP")
  } else if (gen > 1) {
    byBreed <- h %>%
      html_nodes("table.roundy") %>%
      .[[5]] %>%
      html_table(fill = TRUE) %>%
      as_tibble() %>%
      slice(5:nrow(.)) %>%
      select(2:6) %>%
      mutate(cat = "Depends on Type")
    
    colnames(byBreed) <- c("Move", "Type", "Pwr.", "Acc.", "PP", "Cat.")
  } else {
    byBreed <- tibble(
      Move = "NA",
      Type = "NA",
      `Pwr.` = "NA",
      `Acc.` = "NA",
      PP = "NA",
      `Cat.` = "NA",
    )
  }
  
  byBreed <- byBreed %>%
    as_tibble() %>%
    mutate(
      Level = "",
      Method = "Breed"
    )
  
  learnset <- bind_rows(byLevel, byMachine, byBreed)
  as_tibble(learnset) %>%
    filter(!str_detect(Type, "(Type|Bold|Move)")) %>%
    mutate(
      `Acc.` = case_when(
        grepl("—", `Acc.`) ~ gsub(".*", "—%", `Acc.`),
        grepl("\\d*}}", `Acc.`) ~ gsub("\\d*}}", "", `Acc.`),
        grepl("\\d{3}[^%]", `Acc.`) ~ gsub("^\\d{3}", "", `Acc.`),
        TRUE ~ `Acc.`
      ),
      `Pwr.` = case_when(
        grepl("—", `Pwr.`) ~ gsub(".*", "—", `Pwr.`),
        grepl("^0", `Pwr.`) ~ substring(`Pwr.`, 4, 5),
        grepl("\\d") ~ substring(`Pwr.`, 0, 3),
        TRUE ~ `Pwr.`
      )
    ) %>%
    select("Move", "Type", "Cat.", "Pwr.", "Acc.", "PP", "Method")
}


View(getLearnset("Bulbasaur", "I"))
View(getLearnset())
View(getLearnset("Magikarp", "II"))
View(getLearnset("Magikarp", "III"))


View(getLearnset("Greninja", "VI"))
View(getLearnset("Gallade", "VII"))
View(getLearnset("Melmetal", "VII"))
#View(getLearnset("Regidrago", "VIII"))
```

Consider different formes:

"Deoxys"     "Wormadam"   "Giratina"   "Shaymin"    "Basculin"   "Darmanitan" "Tornadus"   "Thundurus"  "Landorus"  
"Keldeo"     "Meloetta"   "Flabébé"    "Meowstic"   "Aegislash"  "Pumpkaboo"  "Gourgeist"  "Zygarde"    "Hoopa"     
"Oricorio"   "Lycanroc"   "Wishiwashi" "Minior"  

Test1 : Webscraping [not successful yet]
```{r}
#Deoxys find learnset
h <- read_html("https://pokemondb.net/pokedex/deoxys")

#Type and abilities
h %>% 
  html_node("table.vitals-table") %>% 
  html_nodes("a") %>% 
  html_text()

#Learnset Normal
h %>% 
  html_nodes("table.data-table") %>% 
  .[[2]] %>% 
  html_table()
  
```

#Test2: API calls [success!]
```{r}
romGen <- tibble(arabic = c(1,2,3,4,5,6,7,8),
                 numerals = c("I","II","III","IV","V","VI","VII","VIII"),
                 versions = c("red-blue","gold-silver","ruby-sapphire","diamond-pearl","black-white","x-y","sun-moon","sword-shield"))

#api test
rversion <- GET("https://pokeapi.co/api/v2/version", query = list(limit = 40))
stop_for_status(rversion)
jversion <- content(rversion, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
jversion$results

rvgroups <- GET("https://pokeapi.co/api/v2/version-group", query = list(limit = 40)) 
stop_for_status(rvgroups)
rvgroups <- content(rvgroups, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
rvgroups$results


(rvgroups$results %>% filter(name %in% romGen$versions))
```

# Input: Pokemon, Output: Learnset
```{r}

name = "deoxys-normal"
names = c("deoxys-normal","deoxys-speed","deoxys-attack","deoxys-defense")

r <- GET(str_glue("https://pokeapi.co/api/v2/pokemon/{name}/",name = name))
stop_for_status(r)
j <- content(r, type = "text", encoding = 'UTF-8') %>% fromJSON(flatten = TRUE)

j$moves$move.name
j$moves$move.url

```

# Find Move attributes and past_values
```{r}

r2 <- GET(j$moves$move.url[[5]])
stop_for_status(r2)
j2 <- content(r2, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
j2$name
j2$type
j2$damage_class$name
j2$power
j2$accuracy
j2$past_values

# Iterate through list of names and get learnset
# Iterate through learnset of each name and return data frame of all names

getMoveInfo_api_helper <- function(jcontent,i){
  r2 <- GET(jcontent[[i]])
  stop_for_status(r2)
  j2 <- content(r2, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
  
  #Move, Type, Cat., Pwr. Acc. PP 
  #Missing Method, Level, but given in the following functions
  df <- tibble(Move = j2$name, Type = j2$type$name, `Cat.` = j2$damage_class$name,
               `Pwr.` = j2$power, `Acc.` = j2$accuracy, PP = j2$pp)
  df <- df %>% 
    mutate(`Pwr.` = ifelse(is.null(`Pwr.`),"-",as.character(`Pwr.`)),
           `Acc.` = ifelse(is.null(`Acc.`),"-",as.character(`Acc.`)))
}

(temp <- lapply(1:3, function(i) getMoveInfo_api_helper(j$moves$move.url,i)) %>% bind_rows()) 
```

#getPastValues

```{r}
getPastValues <- function(jcontent,i){
  r <- GET(jcontent[[i]])
  stop_for_status(r)
  j <- content(r, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
  
  tryCatch({
    df <- j$past_values %>% 
      mutate(Name = j$name)
  },error = function(err){
    df <- tibble(accuracy = integer(0),
                 effect_chance = character(0),
                 effect_entries = list(),
                 power = integer(),
                 pp = integer(),
                 type = character(0),
                 version_group.name = character(0))
  })
}

moves <- j$moves$move.url
(test <- lapply(1:length(moves), function(move) getPastValues(moves,move)) %>% bind_rows())
```

#  Complete Function

```{r}
name <- "deoxys-normal"
names <- c("deoxys-normal","deoxys-speed","deoxys-attack","deoxys-defense")


getMoveInfo_api <- function(name){
  
  r <- GET(str_glue("https://pokeapi.co/api/v2/pokemon/{name}/",name = name))
  stop_for_status(r)
  j <- content(r, type = "text", encoding = 'UTF-8') %>% fromJSON(flatten = TRUE)
  
  n <- nrow(j$moves)
  df <- lapply(1:n, function(i) getMoveInfo_api_helper(j$moves$move.url,i)) %>% bind_rows()
  df <- df %>% 
    mutate(Name = name)
}

getMoveInfo_api_helper <- function(jcontent,i){
  r2 <- GET(jcontent[[i]])
  stop_for_status(r2)
  j2 <- content(r2, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
  
  #Move, Type, Cat., Pwr. Acc. PP 
  #Missing Method, Level, but given in the following functions
  df <- tibble(Move = j2$name, Type = j2$type$name, `Cat.` = j2$damage_class$name,
               `Pwr.` = j2$power, `Acc.` = j2$accuracy, PP = j2$pp)
  df <- df %>% 
    mutate(`Pwr.` = ifelse(is.null(`Pwr.`),"-",as.character(`Pwr.`)),
           `Acc.` = ifelse(is.null(`Acc.`),"-",as.character(`Acc.`)))
}



cl <- makeCluster(4)

clusterExport(cl, c('names', 'getMoveInfo_api','getMoveInfo_api_helper'))
clusterEvalQ(cl,{
  library(tidyverse)
  library(httr)
  library(rvest)
  library(jsonlite)
  library(parallel)
  NULL
})




(temp <- parLapplyLB(cl,names, function(name) getMoveInfo_api(name)) %>% bind_rows())
stopCluster(cl)

```

# find move details by version

```{r}
j$moves$move.name %>% .[[move_ind]]
j$moves$version_group_details %>% .[1:10] %>% .[[move_ind]] %>% select(1,2,4)


getLearnset_api <- function(name){
  r <- GET(str_glue("https://pokeapi.co/api/v2/pokemon/{name}/",name = name))
  stop_for_status(r)
  j <- content(r, type = "text", encoding = 'UTF-8') %>% fromJSON(flatten = TRUE)
  n_move <- length(j$moves$move.name)
  
  df <- lapply(1:n_move, function(i){
    move <- j$moves$move.name %>% .[[i]]
    
    j$moves$version_group_details %>% 
    .[[i]] %>% 
    select(1,2,4) %>% 
    mutate(Move = move,
           Name = name)
  }) %>% bind_rows() %>% 
    select(5,1,4,2,3)
  
}

d_norm <- (getLearnset_api(name))
d_norm %>% 
  filter(`version_group.name` == "ruby-sapphire")

deoxys_formes <- lapply(names, function(x) getLearnset_api(x)) %>% bind_rows()

deoxys_formes %>% 
  filter(Name == "deoxys-speed") %>% 
  filter(version_group.name == "emerald")
```

# Combind Move Info, Pokemon move version info, Pokemon past move versions info

```{r}
# Combine with attack info
(deoxys_moves <- left_join(temp,deoxys_formes,by = c("Move", "Name")))

deoxys_moves %>% 
  filter(Name == "deoxys-normal", version_group.name == "ruby-sapphire")
```

# Find names in API calls
```{r}
load('allMons.6.2020.RData')
allMons

r_api_names <- GET("https://pokeapi.co/api/v2/pokemon", query = list(limit = 897))
stop_for_status(r_api_names)

j_api_names <- content(r_api_names, as = "text") %>% fromJSON()
Api_Names <- j_api_names$results$name %>% gsub("-"," ",.) %>% str_to_title()
df <- tibble(Id = 1:length(Api_Names), Name = Api_Names)

(temp <- left_join(df, allMons))

sum(is.na(allMons))
sum(is.na(df))

sum(is.na(temp))
temp[which(is.na(temp$Gen)),]

```

