```{r, message = FALSE}
library(tidyverse)
library(httr)
library(rvest)
library(jsonlite)
library(parallel)

library(XML)
```

# Text Approach
# Note: Good until gen 3 (w/o Category)
```{r}
mon <- "MelMetal"
gen <- "VII"

romGen <- tibble(arabic = c(1,2,3,4,5,6,7,8),
                 roman = c("I","II","III","IV","V","VI","VII","VIII"),
                 versions = c("red-blue","gold-silver","ruby-sapphire","diamond-pearl","black-white","x-y","sun-moon","sword-shield"))

getLearnset_txt <- function(mon, gen) {
  h <- read_html(str_glue("https://bulbapedia.bulbagarden.net/w/index.php?title={Mon}_(Pok%C3%A9mon)/Generation_{gen}_learnset&action=edit", Mon = mon, gen = gen))
  
  gen_arabic <- romGen %>% filter(numerals == gen) %>% pull(arabic)
  
  if(gen_arabic > 3){
    gen_colnames <- c("Level","Move", "Type", "Cat.", "Pwr.", "Acc.", "PP")
    tutor_colnames <- c("Move","Type","Cat.","Pwr.","Acc.","PP")
  }else{
    gen_colnames <- c("Level","Move", "Type", "Pwr.", "Acc.", "PP")
    tutor_colnames <- c("Move","Type","Pwr.","Acc.","PP")
  }

  learnset <- h %>%
    html_nodes("textarea") %>%
    html_text() %>%
    strsplit("\\n") %>%
    .[[1]]

  # Level
  byLevel <- learnset %>%
    str_subset("level") %>%
    str_extract("(?<=\\{\\{learnlist/level\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, gen_colnames, sep = "\\|", extra = "drop") %>%
    mutate(Method = "Level")

  byMachine <- learnset %>%
    str_subset("tm") %>%
    str_extract("(?<=\\{\\{learnlist/tm\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, gen_colnames, sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Machine")
  
  byBreed <- learnset %>%
    str_subset("breed") %>%
    str_extract("(?<=\\{\\{learnlist/breed\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>% 
    gsub("\\{\\{.*\\}\\}","",.)%>%
    as_tibble() %>%
    separate(value, gen_colnames, sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Breed")

  byTutor <- learnset %>%
      str_subset("tutor") %>%
      str_extract("(?<=\\{\\{learnlist/tutor\\d\\|).*(?=\\}\\})") %>%
      str_subset("NA", negate = TRUE) %>%
      as_tibble() %>%
      separate(value, tutor_colnames, sep = "\\|", extra = "drop") %>%
      mutate(Level = "", Method = "Tutor")

  byEvent <- learnset %>%
    str_subset("event") %>%
    str_extract("(?<=\\{\\{learnlist/event\\d\\|).*(?=\\}\\})") %>%
    gsub("\\{\\{.*\\}\\}","",.) %>% 
    gsub("\\[.*\\]","",.) %>% 
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, gen_colnames, sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Tutor", 
           temp = NULL, temp2 = NULL, 'Event Mon' = NULL)

  df <- bind_rows(byLevel, byMachine, byBreed, byTutor, byEvent) %>% 
    mutate(
      Pwr. = case_when(
        Pwr. == "&mdash;" ~ "-",
        TRUE ~ Pwr.
      ),
      Acc. = case_when(
        Acc. == "&mdash;" ~ "-",
        TRUE ~ Acc.
      )
    ) %>% 
    filter(Type %in% allTypes)
}

(getLearnset_txt("Ralts","III"))
(getLearnset_txt("Melmetal","VII"))
```

getLearnset_text
Gen 1, 2, 3 [success]

```{r}
#For Gen 2 and 3

# postponse
(byBreed <- learnset %>%
    str_subset("breed") %>%
    str_extract("(?<=\\{\\{learnlist/breed\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>% 
    gsub("\\{\\{.*\\}\\}","",.)%>%
    as_tibble() %>%
    separate(value, c("Level", "Move", "Type", "Pwr.", "Acc.", "PP"), sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Breed"))

(byTutor <- learnset %>%
    str_subset("tutor") %>%
    str_extract("(?<=\\{\\{learnlist/tutor\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, c("Level", "Move", "Type", "Pwr.", "Acc.", "PP"), sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Tutor"))

(byEvent <- learnset %>%
    str_subset("event") %>%
    str_extract("(?<=\\{\\{learnlist/event\\d\\|).*(?=\\}\\})") %>%
    gsub("\\{\\{.*\\}\\}","",.) %>% 
    gsub("\\[.*\\]","",.) %>% 
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, c("Level", "Move", "Type","Pwr.","Acc.","PP"), sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Tutor", 
           temp = NULL, temp2 = NULL, 'Event Mon' = NULL))

c("1 piece", "2 pieces", "3") %>% 
str_extract( "\\d+(?! pieces?)")
```

```{r}
# For gen 4 and beyond
gen_4_8_colnames <- c("Level", "Move", "Type", "Cat.", "Pwr.", "Acc.", "PP")

(byLevel <- learnset %>%
    str_subset("level") %>%
    str_extract("(?<=\\{\\{learnlist/level\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, gen_4_8_colnames, sep = "\\|", extra = "drop") %>%
    mutate(Method = "Level"))

(byMachine <- learnset %>%
  str_subset("tm") %>%
  str_extract("(?<=\\{\\{learnlist/tm\\d\\|).*(?=\\}\\})") %>%
  str_subset("NA", negate = TRUE) %>%
  as_tibble() %>%
  separate(value, gen_4_8_colnames, sep = "\\|", extra = "drop") %>%
  mutate(Level = "", Method = "Machine"))

(byBreed <- learnset %>%
  str_subset("breed") %>%
  str_extract("(?<=\\{\\{learnlist/breed\\d\\|).*(?=\\}\\})") %>%
  str_subset("NA", negate = TRUE) %>% 
  gsub("\\{\\{.*\\}\\}","",.)%>%
  as_tibble() %>%
  separate(value, gen_4_8_colnames, sep = "\\|", extra = "drop") %>%
  mutate(Level = "", Method = "Breed"))

(byTutor <- learnset %>%
    str_subset("tutor") %>%
    str_extract("(?<=\\{\\{learnlist/tutor\\d\\|).*(?=\\}\\})") %>%
    str_subset("NA", negate = TRUE) %>%
    as_tibble() %>%
    separate(value, gen_4_8_colnames, sep = "\\|", extra = "drop") %>%
    mutate(Level = "", Method = "Tutor"))

(byEvent <- learnset %>%
  str_subset("event") %>%
  str_extract("(?<=\\{\\{learnlist/event\\d\\|).*(?=\\}\\})") %>%
  gsub("\\{\\{.*\\}\\}","",.) %>% 
  gsub("\\[.*\\]","",.) %>% 
  str_subset("NA", negate = TRUE) %>%
  as_tibble() %>%
  separate(value, gen_4_8_colnames, sep = "\\|", extra = "drop") %>%
  mutate(Level = "", Method = "Tutor", 
         temp = NULL, temp2 = NULL, 'Event Mon' = NULL))
```

#categories for generations before gen 4
```{r}
specTypes <- tibble(Types = c("Dark", "Dragon", "Electric", "Fire", "Grass", "Ice", "Psychic", "Water")) %>% 
  mutate(Cat. = "Special/Status")

physTypes <- tibble(Types = c("Bug", "Fighting", "Flying", "Ghost", "Ground", "Normal", "Poison", "Rock", "Steel")) %>% 
  mutate(Cat. = "Physical/Status")

(gen1_3_Types <- bind_rows(specTypes,physTypes))
```
# special cases for Pokemon with multiple formes

"Deoxys"     "Wormadam"   "Giratina"   "Shaymin"    "Basculin"   "Darmanitan" "Tornadus"   "Thundurus"  "Landorus"  
"Keldeo"     "Meloetta"   "Flabébé"    "Meowstic"   "Aegislash"  "Pumpkaboo"  "Gourgeist"  "Zygarde"    "Hoopa"     
"Oricorio"   "Lycanroc"   "Wishiwashi" "Minior"  
```{r}

```