#Cannot webscrape Serebii

```{r, message = FALSE}
library(tidyverse)
library(jsonlite)
library(lubridate)
library(httr)
library(rvest)

#library(parallel)

load("api.6.2020.RData")
```


# Variables
- Generation Dex

- list of learnsets by Pokemon in GEN 3
  -(https://bulbapedia.bulbagarden.net/wiki/Grovyle_(Pok%C3%A9mon)/Generation_III_learnset#By_leveling_up)
  
  -create a list of learnsets by Pokemon [Not Done]
   - do API requests, make relational data frames

- list of available Pokemon by story/game progression/routes
  -(https://bulbapedia.bulbagarden.net/wiki/Appendix:Emerald_walkthrough/Section_1)

- location filters

- list of learnsets by evolution

- locations for gen7 and gen8

# 1. Gen Dex
```{r}
#eMons - list of every Pokemon in emerald with types and evolutions, potentially with japanese names and field notes
romGen <- tibble(arabic = c(1,2,3,4,5,6,7,8),
                 roman = c("I","II","III","IV","V","VI","VII","VIII"),
                 versions = c("red-blue","gold-silver","ruby-sapphire","diamond-pearl","black-white","x-y","sun-moon","sword-shield"))

genNo = "VI"

getGenMons_info <- function(genNo){
  h <- read_html(str_glue("https://en.wikipedia.org/wiki/List_of_generation_{num}_Pok%C3%A9mon", num = genNo), encoding = "UTF-8")
  
  gen_arabic <- romGen %>% filter(roman == genNo) %>% pull(arabic)
  
  
  if(gen_arabic == 2){
    genMons <- h %>%
      html_nodes("table") %>%
      .[[1]] %>%
      html_table(fill = TRUE) %>%
      as.data.frame() 
  }else if(gen_arabic < 6){
    genMons <- h %>%
      html_nodes("table") %>%
      .[[2]] %>%
      html_table(fill = TRUE) %>%
      as.data.frame() 
  }else if (gen_arabic == 6){
    temp <- h %>% 
      html_nodes("table") %>% 
      .[[2]] %>% 
      html_table(fill = TRUE) %>% 
      as.data.frame()
    
    megaMons <- h %>% 
      html_nodes("table") %>% 
      .[[3]] %>% 
      html_table(fill = TRUE) %>% 
      as.data.frame()
    
    colnames(megaMons) <- names(temp)
    
    genMons <- bind_rows(temp,megaMons)
    
  }else if(gen_arabic == 7){
    temp <- h %>% 
      html_nodes("table") %>% 
      .[[3]] %>% 
      html_table(fill = TRUE) %>% 
      as.data.frame()
    
    alolaMons <- h %>% 
      html_nodes("table") %>% 
      .[[4]] %>% 
      html_table(fill = TRUE) %>% 
      as_tibble(.name_repair = "unique") %>% 
      mutate(`English name` = paste0(.[[1]]," Alola")) 
    
    colnames(alolaMons) <- names(temp)
    
    genMons <- bind_rows(temp,alolaMons)
  
  }else if(gen_arabic == 8){
    temp <- h %>% 
      html_nodes("table") %>% 
      .[[2]] %>% 
      html_table(fill = TRUE) %>% 
      as_tibble(.name_repair = "unique")
    
    galarMons <- h %>% 
      html_nodes("table") %>% 
      .[[3]] %>% 
      html_table(fill = TRUE) %>% 
      as_tibble(.name_repair = "unique") %>% 
      mutate(`English name` = paste0(.[[1]]," Galar"))
    
    gigantaMons <- h %>% 
      html_nodes("table") %>% 
      .[[4]] %>% 
      html_table(fill = TRUE) %>% 
      as_tibble(.name_repair = "unique") %>% 
      mutate(`English name` = paste0(.[[1]]," Gigantamax"))
    
    colnames(galarMons) <- names(temp)
    colnames(gigantaMons) <- names(temp)
    
    genMons <- bind_rows(temp, galarMons, gigantaMons)
    
  }else{
    genMons <- h %>% 
      html_nodes("table") %>% 
      .[[3]] %>% 
      html_table(fill = TRUE) %>% 
      as.data.frame()
  }
  
  
  colnames(genMons) <- c("Name","Name2","NatNo","Type1","Type2","Evolves","Notes")
  
  
  
  (eMons <- genMons %>%
      slice(2:nrow(.)) %>% 
      select(NatNo, Name, Type1, Type2, Evolves) %>%
      mutate(
        Type2 = case_when(
          Type1 == Type2 ~ "",
          grepl("Fairy", Type2) ~ gsub(".*", "Fairy (Gen 6 and on)", Type2),
          TRUE ~ Type2
        ),
        Evolves = case_when(
          grepl("Gardevoir", Evolves) ~ gsub(".*", "Gardevoir,Gallade",Evolves),
          grepl("Ninjask", Evolves) ~ gsub(".*", "Ninjask,Shedinja", Evolves),
          grepl("Glalie", Evolves) ~ gsub(".*", "Glalie,Frosslass", Evolves),
          grepl("Huntail", Evolves) ~ gsub(".*", "Huntail,Gorebyss", Evolves),
          grepl("\\(", Evolves) ~ gsub(".\\(.*\\)","",Evolves) ,
          grepl("\\[", Evolves) ~ gsub("\\[.*","", Evolves),
          # grepl("(Mega|End|Obs|No|Primal)", Evolves) ~ gsub(".*","", Evolves),
          TRUE ~ Evolves
        ),
        Gen = gen_arabic,
        GenX = genNo
      ) %>%
      distinct(Name, .keep_all = TRUE)) %>% 
    filter(!str_detect(Type1,"(Type(s)|Primary)"))
}


suppressMessages(getGenMons_info("VI"))
(allMons <- lapply(romGen$roman, function(NUM) suppressMessages(getGenMons_info(NUM))) %>% bind_rows)
```

```{r}
allMons <- lapply(c("I","II","III","IV","V","VI","VII","VIII"), function(NUM) getGenMons_info(NUM)) %>% bind_rows

save(allMons, file = "allMons.6.2020.RData")
```


#2. Scrape Learnset

```{r}
#4
mon = "Magikarp"
h2 <- read_html(str_glue("https://bulbapedia.bulbagarden.net/wiki/{mon}_(Pok%C3%A9mon)/Generation_III_learnset#By_leveling_up"), mon = mon)

# By Level



byLevel <- h2 %>% 
  html_nodes("table.sortable") %>% 
  html_table() %>% 
  as.data.frame() %>% 
  select(1:6)

#Fix up values
byLevel <- byLevel %>% 
  mutate(
  `Acc.` = case_when(
    grepl("\\d*}}",`Acc.`) ~ gsub("\\d*}}","",`Acc.`),
    TRUE ~ `Acc.`
  ),
  `Pwr.` = case_when(
    grepl("—",`Pwr.`) ~ gsub(".*","—",`Pwr.`),
    grepl("^0",`Pwr.`) ~ substring(`Pwr.`, 4, 5),
    TRUE ~ substring(`Pwr.`, 0, 3)
  ),
  Level = case_when(
    TRUE ~ as.character(Level))
  )

(byLevel <- byLevel %>% mutate(
  Level = substring(Level, 0, nchar(Level)/2),
  PP = as.character(PP)
) %>% 
  as_tibble())
```

```{r}
byMachine <- h2 %>% 
  html_nodes("table.roundy") %>% 
  .[[3]] %>% 
  html_table(fill = TRUE) %>% 
  as_tibble %>%
  slice(5:nrow(.)) %>% 
  select(3:7) 


colnames(byMachine) <- slice(byMachine,1)
(byMachine <- 
  byMachine %>% 
  as_tibble() %>% 
  mutate(Level = ""))
```

```{r}
byBreed <- h2 %>% 
  html_nodes("table.roundy") %>% 
  .[[5]] %>% 
  html_table(fill = TRUE) %>% 
  as_tibble() %>% 
  slice(5:nrow(.)) %>% 
  select(2:6)

colnames(byBreed) <- slice(byBreed,1)

byBreed <-
  byBreed %>% 
  slice(2:nrow(.)-1) %>% 
  as_tibble() %>% 
  mutate(Level = "")

learnset <- bind_rows(byLevel, byMachine, byBreed)
View(learnset)


```

# Function form of operations above

```{r function}
Mon = "Magikarp"
getLearnset <- function(Mon, gen = "III") {
  h <- read_html(str_glue("https://bulbapedia.bulbagarden.net/wiki/{mon}_(Pok%C3%A9mon)/Generation_{gen}_learnset#By_leveling_up",
    mon = Mon, gen = gen
  ))

  # By Level

  byLevel <- h %>%
    html_nodes("table.sortable") %>%
    html_table() %>%
    as.data.frame() %>%
    select(1, Move, Type, `Pwr.`, `Acc.`, PP)

  colnames(byLevel) <- c("Level", "Move", "Type", "Pwr.", "Acc.", "PP")

  # Fix up values
  byLevel <- byLevel %>%
    mutate(
      `Acc.` = case_when(
        grepl("\\d*}}", `Acc.`) ~ gsub("\\d*}}", "", `Acc.`),
        TRUE ~ `Acc.`
      ),
      `Pwr.` = case_when(
        grepl("—", `Pwr.`) ~ gsub(".*", "—", `Pwr.`),
        grepl("^0", `Pwr.`) ~ substring(`Pwr.`, 4, 5),
        TRUE ~ substring(`Pwr.`, 0, 3)
      ),
      Level = case_when(
        TRUE ~ as.character(Level)
      )
    )

  byLevel <- byLevel %>%
    mutate(
      Level = substring(Level, 0, nchar(Level) / 2),
      PP = as.character(PP),
      Method = "Level"
    ) %>%
    as_tibble()


  # By Machine

  byMachine <- h %>%
    html_nodes("table.roundy") %>%
    .[[3]] %>%
    html_table(fill = TRUE) %>%
    as_tibble() %>%
    slice(5:nrow(.)) %>%
    select(3:7)


  colnames(byMachine) <- slice(byMachine, 1)
  byMachine <-
    byMachine %>%
    as_tibble() %>%
    mutate(
      Level = "",
      Method = "Machine"
    ) 

  byBreed <- h %>%
    html_nodes("table.roundy") %>%
    .[[5]] %>%
    html_table(fill = TRUE) %>%
    as_tibble() %>%
    slice(5:nrow(.)) %>%
    select(2:6)

  colnames(byBreed) <- slice(byBreed, 1)

  byBreed <- byBreed %>%
    as_tibble() %>%
    mutate(
      Level = "",
      Method = "Breed"
    )

  learnset <- bind_rows(byLevel, byMachine, byBreed)
  as_tibble(learnset) %>% 
    filter(!str_detect(Type, "(Type|Bold)"))
}
View(getLearnset("Magikarp"))

```


# 3. Pokemon by Area

 - Sort by region by generation
 - Get locations by region
 - Get location areas by locations
 - Get Pokemon encounters by location - Do through app since multiple areas exist in some locations

# 4.


- scraping
```{r}
a = c("I","II","III")
a <- case_when(
  a == "I" ~ 1,
  a == "II" ~ 2,
  a == "III" ~ 3,
  TRUE  ~ 4
)


r <- GET(str_glue("https://pokeapi.co/api/v2/generation/{id}/", id = 3))
stop_for_status(r)

jen3 <- content(r, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
jen3$pokemon_species
jen3$abilities
jen3$moves

rregions <- GET(str_glue("https://pokeapi.co/api/v2/region/{id}", id = 7))
stop_for_status(rregions)
jregions <- content(rregions, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)

#locations in generation 3
(locations = jregions$locations$name)

rlocations <- GET(str_glue("https://pokeapi.co/api/v2/location/{name}/", name = "alola-route-1")) 
stop_for_status(rlocations)
jlocations <- content(rlocations, type = "text", encoding = "UTF-8") %>%  fromJSON(flatten = TRUE)

location_areas = jlocations$areas$name

rlocation_area <- GET(str_glue("https://pokeapi.co/api/v2/location-area/{name}/", name = location_areas))
stop_for_status(rlocation_area)
jlocation_area <- content(rlocation_area, type = "text", encoding = "UTF-8") %>%  fromJSON(flatten = TRUE)

pokemon_by_area <- jlocation_area$pokemon_encounters$pokemon.name
```
# Find locations without areas and filter them out

```{r}
loc_test <- sapply(locations, function(x) getLocationAreas(x)) 
loc_test[!is.null(loc_test)]
compact(loc_test)
```

# Functions <- Pokemon by location area
- functions, scraping, and clusters
```{r}

getLocations <- function(genNo) {
  genNo <- case_when(
    genNo == "I" ~ 1,
    genNo == "II" ~ 2,
    genNo == "III" ~ 3,
    genNo == "IV" ~ 4,
    genNo == "V" ~ 5,
    genNo == "VI" ~ 6,
    genNo == "VII" ~ 7,
    genNo == "VIII" ~ 8,
    TRUE ~ 0
  )
  rregions <- GET(str_glue("https://pokeapi.co/api/v2/region/{id}", id = genNo))
  stop_for_status(rregions)
  jregions <- content(rregions, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)

  # locations in generation 3
  locs <- jregions$locations$name
}
#list of locations
alolaLoc <- (getLocations("VII"))
```

```{r}
loc = alolaLoc[2]
getLocationAreas <- function(loc){
  rlocations <- GET(str_glue("https://pokeapi.co/api/v2/location/{name}/", name = loc)) 
  stop_for_status(rlocations)
  jlocations <- content(rlocations, type = "text", encoding = "UTF-8") %>%  fromJSON(flatten = TRUE)
  location_areas <- jlocations$areas$name
  
  df <- data.frame(location_areas) %>% mutate(name = loc)
}

(getLocationAreas(alolaLoc[1]))
alolaArea <- sapply(alolaLoc, function(loc) getLocationAreas(loc))
alolaArea2 <- compact()
```

```{r}
getAreaMons <- function(area){
  rlocation_area <- GET(str_glue("https://pokeapi.co/api/v2/location-area/{name}/", name = area))
  stop_for_status(rlocation_area)
  jlocation_area <- content(rlocation_area, type = "text", encoding = "UTF-8") %>%  fromJSON(flatten = TRUE)
  pokemon_by_area <- jlocation_area$pokemon_encounters$pokemon.name %>% gsub("-"," ",.) %>% str_to_title()
  data.frame(pokemon_by_area) %>% 
    rename(Pokemon = pokemon_by_area)
}




cl <- makeCluster(4)
clusterEvalQ(cl, {
  library(tidyverse)
  library(jsonlite)
  library(lubridate)
  library(httr)
  library(rvest)
  NULL
})

clusterExport(cl,c("getLocationAreas","getAreaMons","EmLoc"), envir = environment())




EmLocAreas <- parSapply(cl,EmLoc, function(loc) getLocationAreas(loc))
clusterExport(cl,c("EmLocAreas"), envir = environment())  

stopCluster(cl)

(getAreaMons("petalburg-city-area"))
```

# 4. Categorize and sort
- paste(collapse)
```{r}
#For Emerald, filtering

a <- c("cities/towns","routes","other") 

EmLoc

pattern <- c("(city|town)","(route)")
#16 cities and towns
EmLoc %>% str_subset("(city|town)")
#34 routes
EmLoc %>% str_subset("(route)")
#the rest
EmLoc %>% str_subset("(city|town|route)", negate = TRUE)

EmLoc %>% str_subset("^((?!city|town|route).)*$")

EmLoc %>% str_subset(paste(pattern, collapse = "|"))
```

# 5. Learnset by Evolutions
# Match Evolutions

```{r}
revol <- GET(str_glue("https://pokeapi.co/api/v2/evolution-chain/{id}/", id = 1))
stop_for_status(revol)
jevol <- content(revol, type = "text", encoding = "UTF-8") %>% fromJSON(flatten = TRUE)
jevol$chain$evolves_to$species.name
jevol$chain$evolves_to$evolves_to
```


# 6. Scrape Locations for Gen 7 and 8
- scrape from (PokemonDB)
- possible to get by area, but needs customization per page
- get all pokemon by location (not location area)
```{r}
#reference
alolaLoc <- (getLocations("VII"))

#scraping
h <- read_html("https://pokemondb.net/location#tab-alola")
alolaLinks <- h %>% 
  html_nodes("div#loc-alola") %>% 
  html_nodes("a") %>% 
  html_attr("href")

#test first
h2 <- read_html(paste0("https://pokemondb.net/",alolaLinks[1]))

#all location areas
areas <- h2 %>% 
  html_nodes("h2") %>% 
  html_text()

#pokemon by area
h2 %>% 
  html_nodes("table.data-table") %>% 
  .[[7]] %>% 
  html_table()

# Function - Pokemon by location (not area)

h <- read_html("https://pokemondb.net/location#tab-alola")
alolaLinks <- h %>% 
  html_nodes("div#loc-alola") %>% 
  html_nodes("a") %>% 
  html_attr("href")

getG7Mon <- function(loc_link){
  h <- read_html(paste0("https://pokemondb.net/",loc_link))
  df <- h %>% 
    html_nodes("a.ent-name") %>% 
    html_text() %>% 
    as_tibble()
  df %>% mutate(src = loc_link %>% gsub("(/location/)","",.)) %>% 
    rename(Name = value)
}
alola_byloc <- lapply(alolaLinks,function(link) getG7Mon(link)) %>% bind_rows()
save(alola_byloc, file = "alolaMon.RData")
```

